Final Model Analysis

### 2017-11-13 model fitting/final_model.Rmd
edited final model

```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))
x <- oshitar::variable_setup(out)

@@

#### Variables:

* new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strata(ampm) + sqrt(avg_tag_score) + poly(text_length, degree = 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4)
* device_length has 5 knots since hypothesized that it's a better predictor, others only have 4 (reccomended in Regression Modelling Strategies text)

```{r, echo = FALSE}
# build model on train1 (df set to 5 for all splines at first, but setting tag and newline to 4 minimized AIC and performed best)

trainmodel <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = train1, x = TRUE, y = TRUE)
AIC(trainmodel, k = 2) # 54421.88
trainmodel
```

# formal test of PH assumption 
options(scipen=999)
ph_test <- data.frame(predictors = rownames(cox.zph(trainmodel)$table), cox.zph(trainmodel)$table) 
rownames(ph_test) = NULL
ph_test <- ph_test %>% arrange(p) 
# first term of device_length, Apple Product, Camera, Game Console violate PH (stratifying on new_category decreases predictive ability)

```{r, functions for cv, include = FALSE}
# function to perform cross validation, vars should be string: "new_category + new_user..."
crossval <- function(vars, train, test) {
  formula <- paste("Surv(time_until_answer, answered) ~ ", vars, sep = "")
  model <- rms::cph(as.formula(formula), data = train)

@@

@@

(cv_results <- purrr::map2(trains, tests, ~crossval(vars, .x, .y)))

get_avgmetrics(cv_results)
get_avgdiff(cv_results) # metrics don't change that much between fitting model on training and test data sets
```

@@

```{r, echo = FALSE}
dd <- datadist(x)
options(datadist = "dd")
final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                               contain_unanswered + contain_answered + title_questionmark + 
                               title_beginwh + text_contain_punct + text_all_lower + update + 
                               greeting + gratitude + prior_effort + weekday + strat(ampm) + 
                               sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + 
                               rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
                             data = x, x = TRUE, 
                             y = TRUE, surv = TRUE)
final
  AIC(final, k = 2) # 69945.32

validation <- rms::validate(final, method = "crossvalidation", B = 100, bw = F, dxy = TRUE, u = 0.5)
validation
```

@@

>>>>

```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))
list <- oshitar::variable_setup(out)
x <- list[[1]]
x1 <- as.data.frame(x)

@@

```{r, functions for cv, include = FALSE}
# function for cross validation, vars should be string: "new_category + new_user..."
crossval <- function(vars, train, test) {
  formula <- paste("Surv(time_until_answer, answered) ~ ", vars, sep = "")
  model <- rms::cph(as.formula(formula), data = train)

@@

vars3 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + rcs(avg_tag_score, 5) + rcs(text_length, 4) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4)"

vars1 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + avg_tag_score + text_length + device_length + avg_tag_length + newline_ratio"

@@

(cv_results <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y)))
avg_1 <- get_avgmetrics(cv_results)
avg_1

(cv_results1 <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y)))
avg_2 <- get_avgmetrics(cv_results1)
avg_2

avg_1; avg_2
```

@@

```{r, echo = FALSE}
dd <- datadist(x1)
options(datadist = "dd")
final1 <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                               contain_unanswered + contain_answered + title_questionmark + 
                               title_beginwh + text_contain_punct + text_all_lower + update + 
                               greeting + gratitude + prior_effort + weekday + strat(ampm) + 
                               sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + 
                               rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
                             data = x, x = TRUE, 
                             y = TRUE, surv = TRUE)
final1
AIC(final1, k = 2) # 69945.32
(val <- rms::validate(final1, method = "crossvalidation", bw = F, dxy = TRUE, u = 0.5))

final <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                  contain_unanswered + contain_answered + title_questionmark + 
                  text_contain_punct + text_all_lower + update + prior_effort + weekday + 
                  rcs(avg_tag_score, 5) + rcs(text_length, 4) + rcs(device_length, 5) + 
                  rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), 
                  data = x1, x = TRUE, 
                  y = TRUE, surv = TRUE)
final
AIC(final, k = 2)
```

@@

# formal test of PH assumption 
options(scipen=999)
ph_test <- data.frame(predictors = rownames(cox.zph(finalz)$table), cox.zph(finalz)$table) 
rownames(ph_test) = NULL
ph_test <- ph_test %>% arrange(p) 
# first term of device_length, Apple Product, Camera, Game Console violate PH (stratifying on new_category decreases predictive ability)
